Figures

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Figures.Rmd
created rmd file for figures

---
title             : "Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Subjective values of emotion regulation strategies"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Denise Dörfel"
    orcid         :
    affiliation   : "1"
    role          :
      - Conceptuatlization
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Methodology
      - Writing - review & editing 
affiliation       :
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote        :
abstract          : |
 Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
 In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
 Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
 Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
 Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
 However, SVs of ER strategies have not been determined so far. 
 We present a paradigm that is suitable for determining individual SVs of ER strategies. 
 Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
 Relations of SVs to personality traits will be explored.
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
wordcount         : "XXXXX"
bibliography      : ["ER_ED.bib"]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}
editor_options: 
  markdown: 
    wrap: sentence
---

```{=tex}
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}
```

------------------------------------------------------------------------

```{r setupManuscript, echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
# set knitr options
knitr::opts_chunk$set(out.width = "\\textwidth")

# load libraries
library(here) # for path independent file referencing
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

library(papaja) # APA conform output
library(kableExtra) # for tables in R Markdown
#library(BayesFactor) # for bayes factors

@@

```

```{r child = "TheoreticalBackground.Rmd"}
```

```{r child = "Method.Rmd"}
```

```{r child = "Results.Rmd"}
```

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
\newpage

# Acknowledgements

This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
Applications for the centralized funds will be reviewed in May.
Regardless of whether or not this additional funding will be granted, the study can commence immediately.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

# Competing Interests

The authors declare no competing interests.

```{=tex}
\newpage
\setcounter{figure}{0}
```
# Figures and figure captions

\newpage

@@

# Design Table {#DesignTable}

\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}

\newpage

```{r child = "Supplement.Rmd"}
```

>>>>

---
title: "Figures"
author: "Christoph Scheffel"
output: html_document
---

```{r SetupFigures, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

library(tidyverse)

@@

options(papaja.na_string = "")
```

# Figures and figure captions

@@
